Z-Resonance at LEP

### 2010-07-27 Z0-Publikation/tex/paper-template.tex
event selection fertig

\subsection{ Event selection}
Muons barely interact with any matter, therefore there are only very few
entries in the calorimeter along the track of the muon. This has an immense
discriminating power, because jets ...

>>>>

\subsection{ Event selection}
Muons barely interact with any matter, therefore there are only very few
entries in the calorimeter along the track of the muon. This has an immense
discriminating power, because jets consist of tens of particles due to
hadronization at high energies and the decay of unstable particles inside the
jets.

Due to inefficiencies in energy measurement it is possible that not all the
energy provided by the apparatus can finally be seen. Therefore there are large
uncertainties in jet energy measurements, whereas these uncertainties are
smaller for muonic events. This fact can also be used to distinguish these
events from each other and from background as well. For example if the $Z^0$
decays to two very unstable tauons, these tauons decay very fast. Then two
neutrinos are created, but they cannot be measured, so that their contribution
to the visible energy is missing. The visible part of the tau decays resembles
hadronic events, so it is important to be able to separate this background from
the hadronic signal.

To be able to separate muonic events from background it is suitable to ask for
an angle of almost π, as the $Z^0$ boson should be created almost resting in
the laboratory frame, leading to muons flying back to back. Another selection
for muonic events is possible through the requirement of one muon carrying
about half the energy of the event and the other muon carrying a little less
energy than the first muon, but still more than \SI{40}{\percent} of the event
energy.
